Towards a clearer causal question underlying the association between cancer and dementia

### 2021-10-21 04_reports/manuscript.Rmd
updates

Eligibility criteria included: ages 60 to 70 years at study entry; no history of cancer diagnosis, no history of dementia diagnosis; and free of cognitive decline (defined by a Mini Mental Score <26). Out of 10998 persons who participated at study entry, `r total_n` were considered eligible. Time to cancer diagnosis, time to dementia diagnosis and death status was measured for all participants. All participants were followed from study entry until dementia diagnosis, death or 20 years after their individual baseline date, whichever occurred first. Given that participants from the second sub-cohort were followed for 15 years, we assume that they would have had a similar distribution of dementia risk and mortality as the first subcohort, between year 15 and 20.

>>>>

Eligibility criteria included: ages 60 to 70 years at study entry; no history of cancer diagnosis, no history of dementia diagnosis; and free of cognitive decline (defined by a Mini Mental Score <26). Out of 10998 persons who participated at study entry, `r total_n` were considered eligible. Time to cancer diagnosis, time to dementia diagnosis and death status was measured for all participants. All participants were followed from study entry until dementia diagnosis, death or 20 years after their individual baseline date, whichever occurred first. Given that participants from the second sub-cohort were followed for 15 years, we assume that they would have had a similar distribution of dementia risk and mortality as the first subcohort, between year 15 and 20 of follow-up.
